Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-27 fmics/paper.tex
Paragraph describing one of the main theorems
Not describing any proofs yet...

>>>>

Figure~\ref{fig:theorems} gives a selection of theorems we have proved in HOL, some of which refer to additional constants defined in Figure~\ref{fig:auxdefs}.
Our central result, Theorem~(\ref{output_input_at_update_times}), equates the output of a slice to a sum of consecutive input counts.
More precisely, it says that if slice $n$ was just updated, then the output at tap $x$ is equal to the sum of $((\mathsf{tap}\;n\;x)+1)\times(\mathsf{delay}\;n)$ input values, starting from the input $\mathsf{delay\_sum}\;n$ time steps ago.
In light of Theorem~(\ref{output_last_update}), which says a slice's output stays constant between update times for the slice, Theorem~(\ref{output_input_at_update_times}) characterises all outputs at all times.
Thus, the SRS structure's outputs are exact running sums of the input counts over windows whose sizes depend on the the width of the slice and position of taps.
However, the sums are delayed by the total delay across all previous slices (represented by $\mathsf{delay\_sum}$).
